%\documentclass[12pt,a4paper]{article}

%\usepackage{amsmath,amsfonts,amssymb,cancel}
%\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
%\usepackage{natbib,blindtext}
%\usepackage[colorlinks = true, urlcolor= blue]{hyperref}



%\author{Mohd Hamza}
%\title{\underline{Assignment-3 on LaTex and git}}
%\date{February 03, 2023}

%\begin{document}

%\maketitle

\section*{BS22B003}
Name: Mohd Hamza \\
Roll no:- bs22b003 \\
Github ID:- hamzagithub458

\newcommand\blfootnote[1]{%
\begingroup
\renewcommand\thefootnote{}\footnote{#1}%
\addtocounter{footnote}{-1}%
\endgroup
}

\subsection*{\textbf{The Standard Model Equation}}

\begin{equation}
\boxed{
	\math{L} = - \frac{1}{4} F_{\mu \nu} F^{\mu \nu}+ i \bar{\psi} \cancel{D} \psi + h.c.+ \bar{\psi}_i y_{ij} \psi_j \phi + h.c. + |D_\mu \phi|^2 - V(\phi)	\nonumber\
	}
        \end{equation}
        
\\
 This is the Standard Model Equation which is the most successful theory of all time. \\
 The Standard Model of particle physics is often
 visualised as a table of particles which includes 
 matter particles (quarks and leptons), the force carrying particles (bosons) and the Higgs boson. 
 This equation describes how the universe is made up of these basic particles interacting with each other via 3 fundamental forces of nature and all bound together by a special particle called the Higgs boson. 
 This is the equation of the grand theory that actually represents a collection of several mathematical models and is written in its Lagrangian form. This equation is the pinnacle of 400 years of science and gives the correct answer to hundreds of thousands of experiments.   
 
 
\blfootnote{
\begin{thebibliography}{1}
\bibitem{}
Tanabashi, M., Hagiwara, K., Hikasa, K., Nakamura, K., Sumino, Y., Takahashi, F.,Tanaka, J., Agashe, K., Aielli, G., Amsler, C., Antonelli, M., Asner, D. M., Baer, H., Banerjee, Sw., Barnett, R. M., Basaglia, T., Bauer, C. W., Beatty, J. J., … Belousov, V. I. (2018). Review of Particle Physics. In Physical Review D (Vol. 98, Issue 3). American Physical Society (APS). \url{https://doi.org/10.1103/physrevd.98.030001}
\bibitem{}
\url{https://youtu.be/Unl1jXFnzgo}

\bibitem{}
\url{https://www.businessinsider.com/17-equations-that-changed-the-world-2014-3}

\bibitem{}
\url{https://www.symmetrymagazine.org/article/the-deconstructed-standard-model-equation}
\end{thebibliography}
}

%\end{document}





